Trajipaq_sentiment_cr

### 2023-08-15 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
ajout WGI diff

@@

trajipaq <- trajipaq %>% # création des WGI diff (can-home)
  rowwise() %>%
  mutate(vae_arrival_diff = vae_can - vae_arrival) %>%
  mutate(pve_arrival_diff = pve_can - pve_arrival) %>%
  mutate(gee_arrival_diff = gee_can - gee_arrival) %>%
  mutate(rqe_arrival_diff = rqe_can - rqe_arrival) %>%
  mutate(rle_arrival_diff = rle_can - rle_arrival) %>%
  mutate(cce_arrival_diff = cce_can - cce_arrival)

@@

Trajipaq_sentiment_cr <-
  trajipaq %>%
  filter(Q11 != "Canada")%>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "sentimapp_QC",
         "sentimapp_can_dico",
         "sentimapp_can_long",
         "sentimapp_origine_dico",
         "sentimapp_can_origin",
         "sentimapp_can_origin_N",
         "discrim_score",
         starts_with("vae"),
         starts_with("pve"),
         starts_with("gee"),
         starts_with("rqe"),
         starts_with("rle"),
         starts_with("cce"),
         ends_with("score")
         )

>>>>

trajipaq <- trajipaq %>%
  rowwise() %>%
  mutate(wgi_arrival_diff = wgi_origin_arrival_score - wgi_can_arrival_score) %>%
  mutate(wgi_2021_diff = wgi_origin_2021_score - wgi_can_2021_score)

@@

@@

Trajipaq_sentiment_cr <-
  trajipaq %>%
  filter(Q11 != "Canada")%>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "sentimapp_QC",
         "sentimapp_can_dico",
         "sentimapp_can_long",
         "sentimapp_origine_dico",
         "sentimapp_can_origin",
         "sentimapp_can_origin_N",
         "discrim_score",
         starts_with("vae"),
         starts_with("pve"),
         starts_with("gee"),
         starts_with("rqe"),
         starts_with("rle"),
         starts_with("cce"),
         ends_with("score"),
         ends_with("diff")
         )
